---
title: "carbon.csv"
output: 
  html:
    css: '../assets/codebooks.css'
    df_print: paged
    code_folding: show
theme: "lumen"
highlight-style: "atom-one"
bibliography: '../assets/epsy8252.bib'
csl: '../assets/apa-single-spaced.csl'
---


```{r}
#| include: false
source("../assets/codebook-setup.R")
```


Carbon dioxide emissions are the primary driver of global climate change. Some of the biggest predictors of these emissions include economic growth, industrialization, and urbanization. The data in [carbon.csv](https://raw.githubusercontent.com/zief0002/bespectacled-antelope/main/data/carbon.csv) are from 2017 and include some predictors of carbon dioxide emissions for several countries around the world. The variables are:

- `country`: Country name
- `region`: Region of the world
- `co2`: Carbon dioxide measure from the burning of fossil fuels (metric tons per person)
- `wealth`: A measure of a country's wealth based on its GDP; higher values indicate wealthier countries
- `urbanization`: Annual urban population growth (as a percentage)



### Preview

```{r}
# Import data
carbon = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/bespectacled-antelope/main/data/carbon.csv")

# View data
carbon
```


### References

World Bank (2019). [World Bank open data](https://data.worldbank.org/). 

