---
title: "colleges-bordering-mn.csv"
output: 
  html:
    css: '../assets/codebooks.css'
    df_print: paged
    code_folding: show
theme: "lumen"
highlight-style: "atom-one"
bibliography: '../assets/epsy8252.bib'
csl: '../assets/apa-single-spaced.csl'
---


```{r}
#| include: false
source("../assets/codebook-setup.R")
```


The data in [colleges-bordering-mn.csv](https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/colleges-bordering-mn.csv) contains institutional data for 104 colleges and universities in the five state area (MN, IA, WI, ND, and SD). These data were collected by the Department of Education for the [2013 College Score Card](https://collegescorecard.ed.gov/). The variables are:

- `name`: Name of college/university
- `tuition_in_state`: In-state tuition and fees
- `tuition_out_state`: Out-of-state tuition and fees
- `state`: State postal abbreviation (IA = Iowa, MN = Minnesota, ND = North Dakota, SD = South Dakota, WI = Wisconsin)
- `public`: Dummy-coded variable indicating educational sector (1 = public school, 0 = private school)
- `main`: Dummy-coded variable indicating whether the campus is the school's main campus? (1 = yes, 0 = no)
- `admission`: Admission rate
- `act75`: 75th percentile of the ACT cumulative scores
- `avg_fac_salary`: Average faculty salary (per month)
- `completion`: Four-year completion rate for first-time, full-time students
- `pct_pell`: Percentage of undergraduates who receive a Pell grant

<br />


### Preview

```{r}
# Import Data
colleges = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/colleges-bordering-mn.csv")

# View data
colleges
```

<br />



