---
title: "gapminder.csv"
output: 
  html:
    css: '../assets/codebooks.css'
    df_print: paged
    code_folding: show
theme: "lumen"
highlight-style: "atom-one"
bibliography: '../assets/epsy8252.bib'
csl: '../assets/apa-single-spaced.csl'
---


```{r}
#| include: false
source("../assets/codebook-setup.R")
```


The data in [gapminder.csv](https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/gapminder.csv) contains data on 6 attributes for 193 countries. These data, based on 2017 measures collected by World Bank, were compiled by [gapminder.org](https://www.gapminder.org/) and made available free under the [CC-BY license](https://creativecommons.org/licenses/by/4.0/). The variables are:

- `country`: The name of the country
- `region`: The world region (Africa, Americas, Asia, or Europe)
- `income`: Income per person based on the gross domestic product per person, adjusted for differences in purchasing power (in international dollars, fixed for 2017 prices)
- `life_exp`: Average number of years a newborn child would live if current mortality patterns were to stay the same
- `co2`: Carbon dioxide emissions per person from the burning of fossil fuels (metric tonnes of CO2 per person)
- `co2_change`: Indicator of whether the carbon dioxide emissions per person from the burning of fossil fuels has increased or decreased since 2007 (10 year span)
- `population`: Population of the country, in millions

<br />


### Preview

```{r}
# Import Data
gapminder = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/gapminder.csv")

# View data
gapminder
```

<br />


### References

FREE DATA FROM WORLD BANK VIA GAPMINDER.ORG, CC-BY LICENSE

<br />
