---
title: "keith-gpa.csv"
output: 
  html:
    css: '../assets/codebooks.css'
    df_print: paged
    code_folding: show
theme: "lumen"
highlight-style: "atom-one"
bibliography: '../assets/epsy8251.bib'
csl: '../assets/apa-single-spaced.csl'
---


```{r}
#| include: false
source("../assets/codebook-setup.R")
```



The data, stored in [keith-gpa.csv](https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/keith-gpa.csv) includes three attributes on $n = 100$ 8th-grade students. These data come from @Keith:2015. The attributes are:

- `gpa`: Overall Grade-point average (GPA) in all subjects (on a standard 100-point scale)
- `homework`: Average time spent on homework per week across all subjects (in hours)
- `parent_ed`: Education-level (in years of schooling) for the parent with the highest level of education


<br />


### Preview

```{r}
# Import Data
keith = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/keith-gpa.csv")

# View data
keith
```

<br />


### References

<!-- <p style="padding-left: 50px; text-indent: -50px;"> -->

