---
title: "mn-schools.csv"
output: 
  html:
    css: '../assets/codebooks.css'
    df_print: paged
    code_folding: show
theme: "lumen"
highlight-style: "atom-one"
bibliography: '../assets/epsy8251.bib'
csl: '../assets/apa-single-spaced.csl'
---


```{r}
#| include: false
source("../assets/codebook-setup.R")
```



The data in [mnSchools.csv](https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/mn-schools.csv) were collected from [http://www.collegeresults.org](http://www.collegeresults.org) and contain 2011 institutional data for $n=33$ Minnesota colleges and universities. The attributes include:

- `name`: College/university name
- `grad`: Six-year graduation rate (as a percentage)
- `sector`: Educational sector (Public; Private)
- `sat`: Estimated median composite SAT score (in hundreds)
- `tuition`: Amount of tuition and required fees covering a full academic year for a typical student (in thousands of U.S. dollars)


<br />


### Preview

```{r}
# Import Data
mn = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/mn-schools.csv")

# View data
mn
```


<br />


