---
title: "riverview.csv"
output: 
  html:
    css: '../assets/codebooks.css'
    df_print: paged
    code_folding: show
theme: "lumen"
highlight-style: "atom-one"
bibliography: '../assets/epsy8251.bib'
csl: '../assets/apa-single-spaced.csl'
---


```{r}
#| include: false
source("../assets/codebook-setup.R")
```


The data in [riverview.csv](https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/riverview.csv) come from @Lewis-Beck:2016 and contain five attributes collected from a random sample of $n=32$ employees working for the city of Riverview, a hypothetical midwestern city. The attributes include:

- `education`: Years of formal education
- `income`: Annual income (in thousands of U.S. dollars)
- `seniority`: Years of seniority
- `gender`: Employee's gender
- `party`: Political party affiliation


<br />


### Preview

```{r}
# Import Data
city = readr::read_csv(file = "https://raw.githubusercontent.com/zief0002/rustic-penguin/main/data/riverview.csv")

# View data
city
```

<br />

### References


